# Executive Summary

## Summary of Changes in Assessment Inputs

1. Added catch data: finalized catch (in mt) for 2017-2021, estimated catch biomass through  `r date`.
2. Added design-based Gulf of Alaska Trawl Survey biomass data for 2019 and 2021. 
3. Added Gulf of Alaska Trawl Survey length composition data for 2019 and 2021.
4. Added Fishery length composition data from 2018-2021.
5. Updated all historical data to reflect what is currently available in AFSC and AKFIN databases.
6. Updated aging error matrix using Punt et al. (2008) method for GOA Flathead Sole double reads; previous values were from BSAI FHS.


## Summary of Results
No new models were considered this year.  The previously accepted model, referred to herein as model 17.0a, was updated with new data, as described above, and the modeling software was bridged from Stock Synthesis v3.24u to v3.30.16. The present model is referred to as Model 17.1a.

The key results of the assessment, based on the author’s preferred model (Model 17.1a), are compared to the key results of the accepted 2021 update assessment [@Kapur2021] in the table below.

```{r, child= "01a-main_table.Rmd", eval = T}
```
 * Projections are based on  catches of `r c1` t (through `r date`) used in place of maximum permissible ABC for `r year` and `r c2` t used in place of maximum permissible ABC for `r year+1` and `r year+2`. The 2021 and 2022 catch was estimated as the average of the total catch in each of the last 5 years (`r paste0(c(year-5,year-1), collapse = "-")`). 


```{r, child= "01b-apportionment.Rmd", eval = T}

```

 
