---
editor_options: 
  markdown: 
    wrap: sentence
---

## Harvest recommendations

The reference fishing mortality rate for `r species` is determined by the amount of reliable population information available (Amendment 56 of the Fishery Management Plan for the groundfish fishery of the Bering Sea/Aleutian Islands).
Estimates of $F_{40\%}$, $F_{35\%}$, and $SPR_{40\%}$ were obtained from a spawner-per recruit analysis.
Assuming that the average recruitment from the `r paste0(range(subset(rd_breaks, era == 'Main')[,'yr']),collapse = "-")` year classes estimated in this assessment represents a reliable estimate of equilibrium recruitment, then an estimate of $B_{40\%}$ is calculated as the product of $SPR_{40\%}$ times the equilibrium number of recruits.
Since reliable estimates of the `r year` spawning biomass (B), $B_{40\%}$, $F_{40\%}$, and $F_{35\%}$ exist and B>$B_{40\%}$, the `r species` reference fishing mortality is defined in Tier 3a.
For this tier, $F_{ABC}$ is constrained to be ≤ $F_{40\%}$, and $F_{OFL}$ is defined to be $F_{35\%}$.

Because the `r species` stock has not been overfished in recent years and the stock biomass is relatively high, it is not recommended to adjust $F_{ABC}$ downward from its upper bound.


### Amendment 56 Reference Points

*Specification of OFL and Maximum Permissible ABC*

Tier 3 uses the following reference points: $B_{40\%}$, equal to 40% of the equilibrium spawning biomass that would be obtained in the absence of fishing; $F_{35\%}$, equal to the fishing mortality rate that reduces the equilibrium level of spawning per recruit to 35% of the level that would be obtained in the absence of fishing; and $F_{40\%}$, equal to the fishing mortality rate that reduces the equilibrium level of spawning per recruit to 40% of the level that would be obtained in the absence of fishing.
Estimation of the $B_{40\%}$ reference point requires an assumption regarding the equilibrium level of recruitment.
In this assessment, it is assumed that the equilibrium level of recruitment is equal to the average of age-3 recruitments between 1984 and `r year`.
Other useful biomass reference points which can be calculated using this assumption are $B_{100\%}$ and $B_{35\%}$, defined analogously to $B_{40\%}$.
The `r year+1` estimates of these reference points are shown below. Values are from the projection model for `r base_model_name` and should not be compared directly to outputs from Stock Synthesis forecast outputs.

| Quantity                      | Value |
|-------------------------------|-------|
| Stock Spawning Biomass (2023) |    `r safe[4,4]`   |
|      $B_{40\%,2023}$             |     `r safe[6,4]`    |
|                     $F_{40\%,2023}$           |  `r safe[10,4]`       |
|                        $maxF_{ABC,2023}$        |  `r safe[9,4]`       |
|                               $B_{35\%,2023}$ |     `r safe[7,4]`    |
|               $F_{35\%,2023}$               |    `r safe[8,4]`     |
|                  $F_{OFL,2023}$              |      `r safe[8,4]`   |
|               $ABC_{2023}$                 |    `r safe[12,4]`     |
|                  $OFL_{2023}$              |      `r safe[11,4]`   |

Female spawning biomass for `r year+1` is estimated at  `r safe[4,4]`  t.
This is above the $B_{40\%}$ value of `r safe[6,4]`  t.
Under Amendment 56, Tier 3, the maximum permissible fishing mortality for ABC is $F_{40\%}$ and fishing mortality for OFL is $F_{35\%}$.
Applying these fishing mortality rates yields an ABC in 2023 of `r safe[12,4]` t and an OFL of `r safe[11,4]` t.

### Area Allocation of Harvests

TAC for `r species` in the Gulf of Alaska are divided among four smaller management areas (Western, Central, West Yakutat and Southeast Outside). The area-specific ABC for `r species` in the GOA are divided up over the four management areas by applying the fraction of the survey biomass estimated for each area (relative to the total over all areas) in `r year+1` and `r year+2` from the survey averaging random effects model to the `r year+1` and `r year+2` ABCs, defined above. The area-specific allocations for `r year+1` and `r year+2` are:

```{r}
  
flextable::flextable(appo[,-1]) %>%
     flextable::hline_top(part='all') %>% 
    flextable::hline_bottom() %>%
  flextable::colformat_num(big.mark = ',') %>%
  flextable::colformat_double(i = c(2:3), j = c(3:7), digits = 0)
 
```

### Harvest Projections

A standard set of projections is required for each stock managed under Tiers 1, 2, or 3 of Amendment 56.
This set of projections encompasses seven harvest scenarios designed to satisfy the requirements of Amendment 56, the National Environmental Policy Act, and the Magnuson-Stevens Fishery Conservation and Management Act (MSFCMA).

For each scenario, the projections begin with the vector of `r year` numbers at age as estimated in the assessment.
This vector is then projected forward to the beginning of `r year + 1` using the schedules of natural mortality and selectivity described in the assessment and the best available estimate of total (year-end) catch for `r year`.
In each subsequent year, the fishing mortality rate is prescribed on the basis of the spawning biomass in that year and the respective harvest scenario.
In each year, recruitment is drawnfrom an inverse Gaussian distribution whose parameters consist of maximum likelihood estimates determined from recruitments estimated in the assessment.
Spawning biomass is computed in each year based on the time of peak spawning and the maturity and weight schedules described in the assessment.
Total catch after `r year` is assumed to equal the catch associated with the respective harvest scenario in all years.
This projection scheme is run 1,000 times to obtain distributions of possible future stock sizes, fishing mortality rates, and catches.

Five of the seven standard scenarios will be used in an Environmental Assessment prepared in conjunction with the final SAFE.
These five scenarios, which are designed to provide a range of harvest alternatives that are likely to bracket the final TAC for 2019, are as follow ("$max F_{ABC}$" refers to the maximum permissible value of $F_{ABC}$ under Amendment 56):

-   Scenario 1: In all future years, *F* is set equal to $max F_{ABC}$.
    (Rationale: Historically, TAC has been constrained by ABC, so this scenario provides a likely upper limit on future TACs.)

-   Scenario 2: In `r year` and `r year + 1`, *F* is set equal to a constant fraction of $max F_{ABC}$, where this fraction is equal to the ratio of the realized catches in `r year-3`-`r year-1` to the ABC recommended in the assessment for each of those years.
    For the remainder of the future years, maximum permissible ABC is used.
    (Rationale: In many fisheries the ABC is routinely not fully utilized, so assuming an average ratio catch to ABC will yield more realistic projections.)

-   Scenario 3: In all future years, *F* is set equal to 50% of $max F_{ABC}$.
    (Rationale: This scenario provides a likely lower bound on FABC that still allows future harvest rates to be adjusted downward when stocks fall below reference levels.)

-   Scenario 4: In all future years, *F* is set equal to the 2013-2017 average *F*.
    (Rationale: For some stocks, TAC can be well below ABC, and recent average *F* may provide a better indicator of $F_{TAC}$ than $F_{ABC}$.)

-   Scenario 5: In all future years, *F* is set equal to zero.
    (Rationale: In extreme cases, TAC may be set at a level close to zero.)

Two other scenarios are needed to satisfy the MSFCMA's requirement to determine whether a stock is currently in an overfished condition or is approaching an overfished condition.
These two scenarios are as follows (for Tier 3 stocks, the MSY level is defined as $B_{35\%}$):

-   Scenario 6: In all future years, *F* is set equal to $F_{OFL}$.
    (Rationale: This scenario determines whether a stock is overfished. If the stock is expected to be 1) above its MSY level in 2018 or 2) above ½ of its MSY level in 2018 and above its MSY level in 2028 under this scenario, then the stock is not overfished.)

-   Scenario 7: In `r year` and `r year + 1`, *F* is set equal to max $F_{ABC}$, and in all subsequent years F is set equal to FOFL.
    (Rationale: This scenario determines whether a stock is approaching an overfished condition. If the stock is 1) above its MSY level in 2020 or 2) above 1/2 of its MSY level in 2020 and expected to be above its MSY level in 2030 under this scenario, then the stock is not approaching an overfished condition.)

Spawning biomass, fishing mortality, and yield are tabulated for each of the seven standard projection scenarios (Tables 10.\@ref(tab:projSB) through 10.\@ref(tab:projcatch)).
The difference for this assessment for projections is in Scenario 2 (Author's *F*); we use pre-specified catches to increase accuracy of short-term projections in fisheries where the catch is usually less than the ABC.
This was suggested to help management with setting preliminary ABCs and OFLs for two-year ahead specifications.

In addition to the seven standard harvest scenarios, Amendments 48/48 to the BSAI and GOA Groundfish Fishery Management Plans require projections of the likely OFL two years into the future.
While Scenario 6 gives the best estimate of OFL for `r year`, it does not provide the best estimate of OFL for `r year + 1`, because the mean `r year` catch under Scenario 6 is predicated on the `r year` catch being equal to the `r year` OFL, whereas the actual `r year` catch will likely be less than the `r year` OFL.
The executive summary contains the appropriate one- and two-year ahead projections for both ABC and OFL.


## Risk Table and ABC recommendation

The SSC in its December 2018 minutes recommended that all assessment authors use the risk table when determining whether to recommend an ABC lower than the maximum permissible.
The following template is used to complete the risk table:

```{r}
library(flextable)
library(tidyverse)

data.frame(level = c("Level 1: Normal",
                     "Level 2: Substantially increased concerns",
                     "Level 3: Major Concern",
                     "Level 4: Extreme concern"),
           assess = c("Typical to moderately increased uncertainty/minor unresolved issues in assessment.", 
                      "Substantially increased assessment uncertainty/ unresolved issues.",
                      "Major problems with the stock assessment; very poor fits to data; high level of uncertainty; strong retrospective bias.",
                      "Severe problems with the stock assessment; severe retrospective bias. Assessment considered unreliable."),
           pop = c("Stock trends are typical for the stock; recent recruitment is within normal range.",
                   "Stock trends are unusual; abundance increasing or decreasing faster than has been seen recently, or recruitment pattern is atypical.",
                   "Stock trends are highly unusual; very rapid changes in stock abundance, or highly atypical recruitment patterns.",
                   "Stock trends are unprecedented; More rapid changes in stock abundance than have ever been seen previously, or a very long stretch of poor recruitment compared to previous patterns."),
           enviro = c("No apparent environmental/ecosystem concerns",
                      "Some indicators showing adverse signals relevant to the stock but the pattern is not consistent across all indicators.",
                      "Multiple indicators showing consistent adverse signals a) across the same trophic level as the stock, and/or b) up or down trophic levels (i.e., predators and prey of the stock)",
                      "Extreme anomalies in multiple ecosystem indicators that are highly likely to impact the stock; Potential for cascading effects on other ecosystem components"),
           fish = c("No apparent fishery/resource-use performance and/or behavior concerns",
                    "Some indicators showing adverse signals but the pattern is not consistent across all indicators",
                    "Multiple indicators showing consistent adverse signals a) across different sectors, and/or b) different gear types",
                    "Extreme anomalies in multiple performance  indicators that are highly likely to impact the stock")) %>% 
  flextable() %>% 
    font(fontname = "Times", part = "all") %>% 
    width(j = ~ assess, width = 1.5) %>% 
    width(j = ~ pop, width = 2) %>% 
    width(j = ~ enviro, width = 1.5) %>% 
    width(j = ~ fish, width = 1.5) %>% 
    set_header_labels(level = "",
                    assess = "Assessment-related considerations",
                    pop = "Population dynamics considerations",
                    enviro = "Environmental/ecosystem considerations",
                    fish = "Fishery Performance") %>% 
  font(fontname = "Times", part = "all") %>% 
  fontsize(size = 10) %>% 
  theme_vanilla() %>% 
  italic(part = "header") 
```

The table is applied by evaluating the severity of four types of considerations that could be used to support a scientific recommendation to reduce the ABC from the maximum permissible.
These considerations are stock assessment considerations, population dynamics considerations, environmental/ecosystem considerations, and fishery performance.
Examples of the types of concerns that might be relevant include the following:

1.  "Assessment considerations---data-inputs: biased ages, skipped surveys, lack of fishery-independent trend data; model fits: poor fits to fits to fishery or survey data, inability to simultaneously fit multiple data inputs; model performance: poor model convergence, multiple minima in the likelihood surface, parameters hitting bounds; estimation uncertainty: poorly-estimated but influential year classes; retrospective bias in biomass estimates.
2.  "Population dynamics considerations---decreasing biomass trend, poor recent recruitment, inability of the stock to rebuild, abrupt increase or decrease in stock abundance.
3.  "Environmental/ecosystem considerations---adverse trends in environmental/ecosystem indicators, ecosystem model results, decreases in ecosystem productivity, decreases in prey abundance or availability, increases or increases in predator abundance or productivity.
4.  "Fishery performance---fishery CPUE is showing a contrasting pattern from the stock biomass trend, unusual spatial pattern of fishing, changes in the percent of TAC taken, changes in the duration of fishery openings."

#### Assessment considerations

Overall, the model fits all the data sets very well. Both the survey index, and survey and fishery composition data show no concerning patterns. All parameters were well estimated, without any convergence issues. Adding the new data had a minimal impact on estimated parameters and management quantities, corroborating the general stability of the model found in previous assessments. We therefore conclude there are no increased concerns and set this consideration at level 1.  

#### Population dynamics considerations

The spawning stock biomass has been above target for the entire time period for which there are data (Figure 10.\@ref(fig:BFtrajectory)). The estimated age 3+ biomass has increased steadily since 2010, coincident with more positive than negative recruitment deviations in the last 10 years (Figure 10.\@ref(fig:rects)). Since we have no increased concerns we set the concern level to 1.

#### Ecosystem considerations

xx

#### Fishery performance

This fishery has consistently caught only a small fraction of the ABC for the last 10 years (Figure 10.\@ref(fig:catchvsTAC)). We did not examine CPUE trends nor spatial patterns of fishing. There are no changes in the duration of fishing openings. Altogether, we see no cause for concern and give this consideration a level 1 as well. 

#### Summary and ABC recommendation

```{r}
l1 = "Level 1: No increased concerns"
l2 = "Level 2: Substantially increased concerns"
l3 = "Level 3: Major concern"
l4 = "Level 4: Extreme concern"


data.frame(assess = l1,
           pop = l1,
           enviro = l1,
           fish = l1) %>% 
  flextable() %>% 
    width(j = ~ assess, width = 1.5) %>% 
    width(j = ~ pop, width = 1.5) %>% 
    width(j = ~ enviro, width = 1.5) %>% 
    width(j = ~ fish, width = 1.5) %>% 
    set_header_labels(level = "",
                    assess = "Assessment-related considerations",
                    pop = "Population dynamics considerations",
                    enviro = "Environmental/ecosystem considerations",
                    fish = "Fishery Performance") %>% 
  fontsize(size = 10) %>% 
  font(fontname = "Times", part = "all") %>% 
  italic(part = "header") 
```




