# Tables


| Parameter Name                              | Fishery            | Survey             |
|---------------------------------------------|--------------------|--------------------|
| Peak (age at plateau start)                 | Estimated [1,16]   | Estimated [1,20]   |
| Width of plateau                            | Fixed (30)         | Fixed (30)         |
| Ascending width (log)                       | Estimated [-4,12]  | Estimated [-4,12]  |
| Descending width (log)                      | Fixed (8)          | Fixed (8)          |
| Initial selectivity at age 0                | Fixed (-10)        | Fixed (-10)        |
| Final selectivity at age 29                 | Fixed (15)         | Fixed (15)         |
| Male peak offset                            | Estimated [-15,15] | Estimated [-15,15] |
| Male Ascending width (log) offset           | Estimated [-15,15] | Estimated [-15,15] |
| Male Descending width (log) offset          | Fixed (0)          | Fixed (0)          |
| Male final offset (transformation required) | Fixed (1)          | Fixed (0)          |
| Male apical selectivity                     | Fixed (1)          | Fixed (1)          |

: Table 10.1. Treatment of selectivity parameters for survey and fishery
fleet. Bracketed values indicate parameter bounds, if applicable.


```{r catchbyarea, echo = FALSE, warning = FALSE, message = FALSE}
catch <- read.csv(here('data','catch',paste0(pull_date,'-catch-byArea.csv')))
catch[catch < 1&!is.na(catch)] <- round(catch[catch < 1 & !is.na(catch)],2)
catch[catch > 1&!is.na(catch)] <- round(catch[catch > 1 & !is.na(catch)],0)
catch$Year <- as.character(catch$Year) 

names(catch) <- c('Year','Total Catch (mt)','Western Gulf','Central Gulf','Eastern Gulf')
flextable::regulartable(catch) %>%  
      flextable::set_caption("Commercial catch (t) and management action for northern rockfish in the Gulf of Alaska, 1961-present. The *Description of the catch time series* Section describes procedures use to estimate catch during 1961-1993. Ctach estimates for 1993-2019 are from NMFS Observer Program and Alaska Regional Office updated through October XX, 2020.") %>%
  flextable::colformat_num(big.mark = ",")
```


```{r catchvsharvest}
knitr::kable(data.frame(year = 1999:2000,
                 catch = 1:2), 
             caption = "Summary of key management measures and the time series of catch, ABC, and TAC for northern rockfish in the Gulf of Alaska",
             booktabs = TRUE)
```

\pagebreak

```{r tab2}
flextable::regulartable(data.frame(year = 1999:2000,
                 catch = 1:2)) %>%  
      flextable::set_caption("Commercial catch (t) and management action for northern rockfish in the Gulf of Alaska, 1961-present. The *Description of the catch time series* Section describes procedures use to estimate catch during 1961-1993. Ctach estimates for 1993-2019 are from NMFS Observer Program and Alaska Regional Office updated through October XX, 2020.")
```

\pagebreak
