---
title: "GOA FHS Assessment Base Model (plots & tables)"
author: M Sosa Kapur maia.kapur@noaa.gov
date: November 2022
format: html
toc: true
always_allow_html: true
editor: source
---

Here I make all tables & plots relevant to the report. It is assumed that projections (separate Rmd) have been run. There are some extra plots here used for presentation purposes as well as notes-to-self in case questions arise in review. I roughly tried to generate these in the same order as the document, but there's also a few back-pocket illustrations.

```{r custom plot settings, echo = FALSE}
ggplot2::theme_set(ggsidekick::theme_sleek( base_size = 8))
theme_replace(text= element_text(family = "roboto condensed", size = 8),
              title = element_text(size = 5)) 

require(MetBrewer)
require(ggtext)
require(showtext)

font_add_google("Signika")
font_add_google("Roboto Condensed", "roboto condensed")
showtext_opts(dpi = 320)
showtext_auto(enable = TRUE)

## all colors to use in this document
docPal <- c('black',met.brewer(name = 'Degas',n = 15))
m2017Col <- docPal[1]
baseCol <- "#154B38"
sensPal <- met.brewer(name = 'Demuth',n = 10)[6:10]
fleetPal <- c('goldenrod','dodgerblue2')



```

```{r load model objects, echo = FALSE}

m2017 <- SS_output(here('model_runs','2017-mod'), covar=TRUE, verbose=FALSE, printstats=FALSE) 
m2017_dat <- SS_readdat(file = here('model_runs','2017-mod','goa_flathead_17_dat.dat'))
base_dat <-  SS_readdat(file = here('model_runs','m0_8-newMI-biasAdj','data.ss'))
base_model <- SS_output(here('model_runs','m0_8-newMI-biasAdj'), covar=TRUE, verbose=FALSE, printstats=FALSE) 
# base_thru17 <- SS_output(here('model_runs','m0_8-thru17'), covar=TRUE, verbose=FALSE, printstats=FALSE)
```


# Tuning
In `01_bridging.qmd` we landed on `m0_8-newMI-biasAdj` as the base model. This has all the new data, corrects the historical survey datapoint, and updates the aging error matrix. The parameter hitting bounds is InitialF and we decided to leave that as-is.

The 2017 assessment used the M-I weighting method for weighting individual data sources, and reverted to the number of hauls for the length comps. This was before updates to the Francis weighting method were revisited by Punt for CAAL data.

There are some slight differences in the Nhauls, namely years 2015-2017 were all fixed at 112 in the previous assessment whereas they vary in my dataset. 

The CAAL sample sizes are literally the raw #s across rows. I'd initially thought these were inconsistent because I was including the ghosted marginal ages in the Nsamp summation; when I remove Fleet -2 they're very much in line.Per the SS manual, it's best to present CAAL data sex-separated because then we aren't assuming rigid sex ratios each year.
```{r echo = FALSE}
lencomp_hauls <- m2017_dat$lencomp %>% select(Yr, FltSvy, Nsamp) %>% mutate(src = '2017') %>%
  rbind(base_dat$lencomp %>% select(Yr,FltSvy, Nsamp) %>% mutate(src = 'base')) %>%
  filter(FltSvy != -1) %>%
  mutate(FltSvy = ifelse(FltSvy == 1, 'Fishery','Survey'))
  # tidyr::pivot_wider(., id_cols = c(Yr, FltSvy), names_from = src, values_from = Nsamp)


## note that 17 mod presented males and females yesterday

agecomp_hauls <- m2017_dat$agecomp %>% select(Yr,Gender, FltSvy, Nsamp) %>% mutate(src = '2017') %>%
  rbind(base_dat$agecomp %>% select(Yr,Gender,FltSvy, Nsamp) %>% mutate(src = 'base')) %>%
  filter(FltSvy != -2) %>% ## survey only
  mutate(FltSvy = ifelse(FltSvy == 1, 'Fishery','Survey')) %>%
  group_by(Yr, FltSvy, Gender, src) %>%
  summarise(totNsamp = sum(Nsamp)) %>% 
  arrange(Yr)
  # tidyr::pivot_wider(., id_cols = c(Yr, FltSvy), names_from = src, values_from = Nsamp)




ggplot(lencomp_hauls, aes(x = Yr, y = Nsamp, color = src)) +
  geom_jitter() +
  geom_vline(xintercept = 2017) +
  scale_color_manual(values = fleetPal) +
  facet_wrap(~FltSvy, ncol = 2) +
  labs(title = 'Input Sample Sizes (nhauls) between assessments, length comps')

ggplot(agecomp_hauls, aes(x = Yr, y = totNsamp, color = src)) +
  geom_point() +
  geom_vline(xintercept = 2017) +
  scale_color_manual(values = fleetPal) +
  facet_wrap(~Gender, ncol = 2) +
  labs(title = 'Input Sample Sizes (nhauls) between assessments, age comps',
       subtitle = 'Input Nsamps have been summed across bins')

```

# Generate tables and figures 
Anything not auto-generated by SS_plots needed for doc/presentation. Save in respective folders here.

```{r}
library(akgfmaps)
SEBS <- akgfmaps::get_base_layers(select.region = "bs.south", set.crs = "auto")

## format this based on  https://github.com/afsc-gap-products/akgfmaps/blob/master/R/make_idw_map.R
raw_surv <- readRDS(here('data', 'survey','hippoglossoides_elassodon','Data_Geostat_Hippoglossoides_elassodon.rds')) 

s2021 <- raw_surv%>% 
  mutate( COMMON_NAME = 'Flathead Sole') %>%
  dplyr::select(Year,COMMON_NAME, CPUE_KGHA  = Catch_KG, LATITUDE = Lat, LONGITUDE = Lon) %>%
  dplyr::filter(Year == 2021) %>%
  make_idw_map(region = "goa",
               set.breaks = "jenks",
               in.crs = "+proj=longlat",
               out.crs = "EPSG:3338", # Set output coordinate reference system
               use.survey.bathymetry = FALSE, ## for GOA
               grid.cell = c(20000, 20000)) %>% # 20x20km grid
  add_map_labels() %>% 
  change_fill_color(new.scheme = "green2", show.plot = TRUE) %>%
  create_map_file(file.prefix = NA, 
                            file.path = NA, 
                            try.change_text_size = TRUE, # 12x9 is a pre-defined size
                            width = 12, 
                            height = 9, 
                            units = "in", 
                            res = 300, 
                            bg = "transparent")

s2019 <- raw_surv%>% 
  mutate( COMMON_NAME = 'Flathead Sole') %>%
  dplyr::select(Year,COMMON_NAME, CPUE_KGHA  = Catch_KG, LATITUDE = Lat, LONGITUDE = Lon) %>%
  dplyr::filter(Year == 2019) %>%
  make_idw_map(region = "goa",
               set.breaks = "jenks",
               in.crs = "+proj=longlat",
               out.crs = "EPSG:3338", # Set output coordinate reference system
               use.survey.bathymetry = FALSE, ## for GOA
               grid.cell = c(20000, 20000)) %>% # 20x20km grid
  add_map_labels() %>% 
  change_fill_color(new.scheme = "green2", show.plot = TRUE) #%>%
  # create_map_file(file.prefix = NA, 
  #                           file.path = NA, 
  #                           try.change_text_size = TRUE, # 12x9 is a pre-defined size
  #                           width = 12, 
  #                           height = 9, 
  #                           units = "in", 
  #                           res = 300, 
  #                           bg = "transparent")


p1 <- s2019$plot+theme(legend.position = 'right') 
p2 <- s2021$plot+theme(legend.position = 'right') 

ggsave(Rmisc::multiplot(plotlist = list(p1,p2), cols = 1),
       file = here('figs','2_cpue_maps.png'),
       height = 10, width = 8, dpi = 520)

  akgfmaps::create_map_file(file.prefix = NA, 
                            file.path = here('figures',''),
                            try.change_text_size = TRUE, # 12x9 is a pre-defined size
                            width = 12, 
                            height = 9, 
                            units = "in", 
                            res = 520, 
                            bg = "transparent")

# usa <- map_data("world") 
# ggplot() +
#   ggsidekick::theme_sleek() +
#   geom_polygon(data = usa, aes(x = long, y = lat, group = group)) +
#   coord_quickmap() +
#   scale_x_continuous(expand = c(0,0), limits = c(-180,-130), breaks = seq(-180,-130,10), labels = paste(seq(-180,-130,10), "°W")) +
#   scale_y_continuous(expand = c(0,0), limits = c(52,72), breaks = seq(52,62,2), labels =  paste(seq(52,62,2), "°N")) +
#   geom_point(data = subset(raw_surv, Year == 2021 & mC  > 0), aes(x = Lon, y = Lat, color = log(mC)))
```



# NOT RUN ---
# Numbering convention
Per instructions here, I need to calculate the "ADSB" (comparing biomass between previous and current models, run only with data thru 2017). The ADSB is , so the name of the model I'm presenting follows the minor change template and is called Model 17.0a.

The instructions were a little vague as to whether I was to compare the new model through 2021 with *data* only thru 2017, or the new model with *data & dynamics* thru 2017 only. I assume the latter, but do note that the 2004 survey value has changed. This is model `m0_8-thru17`. In `data.ss`  I changed the endyr to 2017 and commented out any data > 2017. *Perhaps revisit or wait to do this until weights, etc. have been revisited*.



