# Executive Summary

The Gulf of Alaska flathead sole stock is typically assessed every four years and was last assessed in 2022 (Kapur & Monnahan, 2022). In years without a full assessment, we present an executive summary of harvest projections to recommend harvest levels for the next two years. Please refer to the 2022 full stock assessment report for further information regarding the assessment model (available online at https://apps-afsc.fisheries.noaa.gov/Plan_Team/2022/GOAflathead.pdf). 

Flathead sole is assessed using an age-structured model and Tier 3 determination. Thus, the single species projection model was run using parameter values from the accepted 2022 flathead sole assessment model, together with updated catch information for `r this_year-(2:1)`, and estimated catches for `r paste0(c((this_year),(this_year+2)),collapse = '-')` to predict stock status for flathead sole and to make ABC recommendations for those years. Projections are conducted using numbers-at-age for flathead sole from age 3-21+ and historical recruitment of age 3 individuals is used to calculate OFLs and ABCs. 

## Summary of Changes in Assessment Inputs

Changes in input data: The updated information for this harvest projection includes replacing the estimated `r this_year-1` catch with the final catch value from the Alaska Regional Office (https://www.fisheries.noaa.gov/sites/default/files/akro/car110_goa2023.html) (`r prettyNum(round(as.numeric(catchvec[2,2]),0),big.mark = ',')` t), and estimating the `r this_year`-`r this_year+2`  catches. The `r this_year` projected catch was calculated as the current catch as of `r pull_date` added to the average `r format(as.Date(pull_date), "%d %B")` – December 31 catches over the previous `r average_window` years. The `r this_year+1`  and `r this_year+2`  projected catches were calculated as the average catch over the previous `r average_window` years (`r prettyNum(c2,big.mark = ',')` t). These estimated catches for the present and two future years are input in place of *maxABC* for projections, which is appropriate given that recent catches are much less than the maximum ABC for this stock.

## Summary of Results

The ABC for flathead sole is `r prettyNum(abc_25,big.mark = ',')`  t in `r this_year+1`  and `r prettyNum(abc_26,big.mark = ',')` t in `r this_year+2`  and the OFL is `r prettyNum(ofl_25,big.mark = ',')`  t in `r this_year+1`  and `r prettyNum(ofl_26,big.mark = ',')`  t in `r this_year+2`. 


```{r, child= "01a-main_table.Rmd", eval = T}

```

```{r, child= "01b-apportionment.Rmd", eval = T}

```


\newpage